A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2022-03-31 README.Rmd
include nutshell figure after abstract
use relative path for image
add clean rebuild option in makefile
add note in case of unavailible services

@@

@@

```{bash, eval=FALSE}
git pull && make build && make -B DOCKER=TRUE
```

>>>>

```{r, echo=FALSE}
knitr::include_graphics("Images/nutshell.svg")
```

@@

**Note: The build step may fail since services the build relies on are no longer available. In this case, you can download a ready build image from the [GitHub Releases](https://github.com/aaronpeikert/reproducible-research/releases/latest) and use `docker load -i reproducible-research.tar.gz` to load it. Continue with `make all DOCKER=TRUE`**

@@

```{bash, eval=FALSE}
git pull && make rebuild && make -B DOCKER=TRUE
```
